
---
title: "R Programming Assignment"
author: "Team 5"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[CO,CE]{https://github.com/shilpi357/R-Programming-Team-Team-5}
- \fancyfoot[LE,RO]{\thepage}
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages to install 
#```{r}
#install.packages("readxl")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("ggplot2")


#```
#libraries to import
```{r}
library(readxl)
library(tidyr)
library(dplyr)
library(ggplot2)

```
#Reading the input file
```{r}
supermarket_sales <-read.csv(file = "./supermarket_sales.csv")
```
#Print the top 15 rows of your dataset 
```{r}
head(supermarket_sales, 15)
```
#Print the structure of your dataset
```{r}
str(supermarket_sales)
```
#List the variables in your dataset 

```{r}
names(supermarket_sales)
```
#Identify and remove duplicated data in your dataset

```{r}
data_unique <- supermarket_sales[!duplicated(supermarket_sales), ]
data_unique
```
#Reorder multiple rows in descending order
```{r}
arrange(supermarket_sales, desc(City), desc(Quantity))
```
#Rename some of the column names in your dataset 

```{r}
names(supermarket_sales)[names(supermarket_sales) == "Invoice.ID"] <- "Invoice_ID"
names(supermarket_sales)[names(supermarket_sales) == "CUstomer.type"] <- "Customer_type"
names(supermarket_sales)[names(supermarket_sales) == "Unit.price"] <- "Unit_price"
names(supermarket_sales)[names(supermarket_sales) == "Product.line"] <- "Product_line"
```
#Add new variables in your data frame by using a mathematical function (for e.g. – multiply an existing column by 2 and add it as a new variable to your data frame) 
```{r}

supermarket_sales %>% mutate(Total_price_before_tax = Unit_price * Quantity)
```
#Create a training set using random number generator engine
```{r}
set.seed(1234)
supermarket_sales %>% sample_frac(0.05, replace = FALSE)
```
#Summary Statistics of dataset:-
```{r}
summary(supermarket_sales) 
```

#Plot a bar plot for any 2 variables in your dataset 
```{r}
x = supermarket_sales$Quantity
y = supermarket_sales$Rating
corranswe = cor(x,y,method = "pearson")
corranswe
```
#Find the correlation between any 2 variables by applying least square linear regression model
```{r}
ggplot2::ggplot(data = supermarket_sales, ggplot2::aes(x = Quantity)) + ggplot2::geom_bar(fill = "turquoise")
ggplot2::ggplot(data = supermarket_sales, ggplot2::aes(y = Rating)) + ggplot2::geom_bar(fill = "lawngreen")
```

#Identify the dependent & independent variables and use reshaping techniques and create anew data frame by joining those variables from your dataset
```{r}
Indep <- data.frame(supermarket_sales[,(colnames(supermarket_sales) %in% c("Invoice.ID","Branch","City","Customer.type","Gender","Product.line","Date","Time","Payment"))])

Dep <- data.frame(supermarket_sales[,(colnames(supermarket_sales) %in% c("Unit.price","Quantity","Tax.5.","Total","cogs","gross.margin.percentage","gross.income","Rating"))])
```
#Remove missing values in your dataset.
```{r}
Indep <- na.omit(Indep)

Dep <- na.omit(Dep)
```

#Use any of the numerical variables from the dataset and perform the following statistical functions
#• Mean 
#• Median 
#• Mode 
#• Range 
```{r}

mean(supermarket_sales$Total)

```
```{r}
median(supermarket_sales$Total)
```
```{r}
mode(supermarket_sales$Total)
```
```{r}
range(supermarket_sales$Total)
```

#Plot a scatter plot for any 2 variables in your dataset

```{r}
ggplot(data=supermarket_sales,aes(x=Total,y=cogs))+geom_point(fill="lawngreen")
```
#Write a user defined function using any of the variables from the data set
```{r}
does_city_exist <- function(city_name){
the_values <- supermarket_sales$City
 city_name %in% the_values
}
does_city_exist('City name')
```
#Use data manipulation techniques and filter rows based on any logical criteria that exist in your dataset
```{r}
supermarket_sales %>% filter(Branch == "B" & Rating >= 8)

```




